\documentclass[10pt]{article}
\usepackage{array, xcolor, lipsum}
\usepackage[margin=3cm]{geometry}

%\title{Jack Ellis}
\date{}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\begin{document}
%\maketitle
\vspace{1em}
\begin{minipage}[ht]{0.48\textwidth}
  \begin{flushleft}
    Flat 104, The Habitat\\
        Nottingham\\
        NG1 1GJ
  \end{flushleft}
\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
  \begin{flushright}
    email: jackellis1504@gmail.com\\
        tel: 07948437374\\
        git: github.com/GingertronMk1
  \end{flushright}
\end{minipage}

\section*{Profile}
I am a Computer Science graduate with a 2:1 MSci.
I have excellent communication and administrative skills developed from being a member of a number of committees during my time at the University of Nottingham.
I am a strong worker under pressure, able to quickly make decisions based on information available to me, and I have a good ability to convert someone's request into a more technical format, whatever that format might be.
I am also a strong collaborator within a team, and am always keen to share any experience, tips, or tricks with those who need or want them in order for the team I am a part of to be as strong as it can be.

\section*{Education}
\begin{tabular}{L!{\VRule}R}
  2015--2019&\bf University of Nottingham, MSc Computer Science, 2:1\\
                 &Modules including:\\
                 &- C++ Programming (77\%)\\
                 &- Fundamentals of Information Visualisation (83\%)\\
                 &- Software Engineering Group Project (90\%)\\
                 &- Individual Programming Project (70\%)\\[5pt]
    2013--2015&{\bf Beverley Joint 6th Form, A-Levels}\\
              &Maths A\\
              &Physics B\\
              &Chemistry B\\
\end{tabular}

\section*{Experience}
\begin{tabular}{L!{\VRule}R}
  2020--present&   \bf Developer, We Are Sweet\\
    & I am presently responsible for the maintenance and expansion of a large ticketing website built using Yii2.\par

   \\

  2019--2020&   \bf Back-End Developer, Fifteen Design\\
    & I was responsible for the development and maintenance of a number of php-based websites, built using WordPress, Laravel, and Symfony.\par

   I was initially responsible for the creation of a brochure site for Birch Bedrooms, taking a design from a series of InVision drawings and converting them into a full responsive Wordpress site, liaising with the designer about any issues or inconsistencies that I noticed during the process.\par

   I was also tasked with updating the website for Birmingham Metropolitan College with new features to add to their application system - this website made heavy use of custom Wordpress plugins for which there was no real documentation, as well as a bridge API to pass data back and forth to their custom student/course management system, Unit-e.\\

   \\

    2019--2019&\bf Web Developer, Imaginaire Digital\\
    & Here I was jesponsible for the development of a client website using Wordpress and a custom theme, as well as an internal dashboard system built in Laravel and Laravel Nova. Also involved in creating automation scripts for easier creation of development environments.\\

\end{tabular}

\section*{Technical Skills/Projects}

Programming Languages: C++, CSS/SASS, Haskell, HTML, JavaScript, PHP, SQL\\
Libraries/APIs/Frameworks: Bootstrap, d3, jQuery, OpenGL, Vue, Laravel, Symfony, Yii2\\
Development Environments: GitHub, IntelliJ, MS Visual Studio, vi

\vskip 5mm

In addition to the projects I worked on as part of my degree (which can be found under the \emph{Time} repository in the GitHub link above) I am also a contributor to the Nottingham New Theatre History Project, mostly in a data entry role.
As well as this I created a website designed to show statistics and information about the links between actors at the Nottingham New Theatre, available at \verb|gingertronmk1.github.io|, using JavaScript and the d3 library.

\par

For my Master's dissertation (in the \emph{Dissertation} repository in the GitHub link above) I recreated the game \emph{Frogger} using the Haskell functional programming language.
Within this I gathered requirements, created a development plan, and implemented an object-oriented approach in the functional language.
I carried out user testing and adjusted various aspects of the game based upon feedback from the test subjects, as well as making use of the Travis CI suite.

\section*{Additional Experience and Extracurriculars}

As well as working towards my degree I am also a member of a number of societies, including University Radio Nottingham, the Nottingham New Theatre, and the Improv Society.\\

At URN I was on their committee as Head Of Drama, responsible for overseeing all dramatic content produced by the station in that time.
This required that I organise large groups of people into the same studio at the same time in order to record the audio, and then edit it down into something amusing.\\

Within the New Theatre I have been on their committee for the last year and a half in a backstage capacity, with my role as Company Set Technician requiring me to take a designer's ideas and turn them into something real within the bounds of what is feasible.
I am responsible for ensuring that anything that needs building is done in a safe and efficient manner, and also for assigning people to assistant roles based on known skill sets.
As part of a broader backstage team I have developed good teamworking skills extending to the ability to take a leadership role where appropriate.
As well as this I have been in a number of shows, which has led to my being able to take direction and adjust what I am doing quickly in accordance with what a director believes is better for a role.\\

With the Improv Society I have gained valuable experience speaking in front of large groups of people and making quick, well-justified decisions in a short time-frame.
Within this society I was also elected Publicity and Media Officer, in charge of the public face of the society and attracting audiences to shows.\\

During the summer of 2014 I volunteered at the Centre for Digital Innovation in Hull (C4DI).
Whilst there my project, together with a colleague, was to research the concept of smart cities in other countries and how their technologies could work in Hull, City of Culture 2017.
This culminated in producing and presenting a slide show presentation for the bosses of the C4DI, the information from which was going to be presented to the local council.
Whilst there I also developed a website for one of the founders of the C4DI, which traced people's fast food litter and marked on a map where it was alongside a picture and a comment.

\end{document}
