\title{Curriculum Vitae}
\author{
  Jack Ellis \\
  jackellis1504@gmail.com\\
}
\date{}
\documentclass[12pt, a4paper]{article}

\begin{document}
\pagenumbering{gobble}

\begin{minipage}[c]{.5\textwidth}
  \raggedright
  73 Lenton Boulevard\\
  Nottingham\\
  NG7 2FQ
\end{minipage}
\begin{minipage}[c]{.5\textwidth}
  \raggedleft
  email: jackellis1504@gmail.com\\
  tel: 07891462107
\end{minipage}

\vspace{5mm}

\section*{Profile}
I am a second year Computer Science student studying for my MSc at the University of Nottingham.
I have skills transferable to the workplace which include team working, effective communication, time management, adaptability, determination, and being able to take direction.

\section*{Education}
\begin{tabular}[c]{p{2.5cm}|p{20cm}}
  2015-present  & \textbf{University of Nottingham, MSc Computer Science}
                \\
                & Modules Including:
                \\
                & Systems and Architecture
                \\
                & Programming Paradigms
                \\
                & Introduction To Software Engineering
                \\ \\
  2013-2015     & \textbf{Beverley Joint 6\textsuperscript{th} Form, A-Levels}
                \\
                & Maths A
                \\
                & Physics B
                \\
                & Chemistry B
                \\ \\
  2011-2013     & \textbf{Beverley Grammar School}
                \\
                & 8 GCSEs including Science A*, Maths *, and English A \& B
                \\
\end{tabular}
\\[10pt]
As well as working towards my degree I am also a member of a number of societies, including URN, the Nottingham New
Theatre, and Improv Society.\\
\\
With the Improv Society I have gained valuable experience speaking in front of large groups of people.
I successfully auditioned to be part of a small troupe of 6 people, and spent 9 months planning and preparing for a show we took to Edinburgh Fringe 2016.
I feel this honed my organisational skills, taught me how to take direction and constructive criticism and showed determination to make the show work.
I also find active listening a useful skill in group work.
Within this society I was also elected Publicity and Media Secretary.
I like that you have to make decisions quickly and work as part of a team.\\
\\
At URN I ran a show entitled 'On Call' for a year, in which I filled in if people were unable to present their shows
last-minute. This meant I had to be prepared with a show to go at any time, leading me to prepare up to 3 shows in
advance. I was also elected Head Of Drama for 2017-18, meaning I will be overseeing the dramatic content of URN for this
time.\\
\\
Within the New Theatre, as well as acting in one of their Edinburgh Fringe 2017 shows, I have been elected Workshop
Manager for 2017-18, meaning I will be responsible for the set design and construction for all shows that happen in this
period, as well as maintaining and training for all tools currently in use in the workshop.\\
\\
During the summer of 2014 I volunteered at the Centre for Digital Innovation in Hull (C4DI).
Whilst there my project, together with a colleague, was to research the concept of smart cities in other countries and how their technologies could work in Hull, City of Culture 2017.
This culminated in producing and presenting a slide show presentation for the bosses of the C4DI, the information from which was going to be presented to the local council.
Whilst there I also developed a website for one of the founders of the C4DI.\\

\end{document}
